---
title: "Western Electric Company Rules (WECO) for Shewhart Control Chart"
author: ""
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Simulation

We simulate normally distributed data as follows:

```{r, eval=T, echo=TRUE}
require(weco);
set.seed(10000);
n.sim     <- 50000;
sdx       <- 2;
simu.data <- rnorm(n.sim, sd = sdx);
quants    <- c(0.25, 0.5, 0.75);
xmax      <- 3000;
ymax      <- 0.015;
```

## Single rule

### Rule 1

1 point $>L$ standard deviations from center line

```{r, eval=T, echo=TRUE, fig.width=6, fig.height=5}
l          <- 3;
rst.1      <- weco.rule(rule=1, x=simu.data, l=l, sdx=sdx, mux=0);
simu.arl   <- weco.rl(rst.1);
hist(simu.arl, breaks = 100, freq = F,
     xlim=c(0, xmax), ylim=c(0,ymax),
     xlab="Running Length", ylab="Probability", main="Rule 1");
```

### Rule 2

$K$ points in a row on the same side of the center line 

```{r, eval=T, echo=TRUE, fig.width=6, fig.height=5}
k          <- 9;
rst.2      <- weco.rule(rule=2, x=simu.data, k=k, sdx=sdx, mux=0);
simu.arl   <- weco.rl(rst.2);
hist(simu.arl, breaks = 100, freq = F,
     xlim=c(0, xmax), ylim=c(0,ymax),
     xlab="Running Length", ylab="Probability", main="Rule 2");
```

### Rule 3

$K$ points in a row, all increasing or decreasing


```{r, eval=T, echo=TRUE, fig.width=6, fig.height=5}
k          <- 6;
rst.3      <- weco.rule(rule=3, x=simu.data, k=k, sdx=sdx, mux=0);
simu.arl   <- weco.rl(rst.3);
hist(simu.arl, breaks = 100, freq = F,
     xlim=c(0, xmax), ylim=c(0,ymax),
     xlab="Running Length", ylab="Probability", main="Rule 3");
```

### Rule 4

$K$ points in a row, alternating up and down 

```{r, eval=T, echo=TRUE, fig.width=6, fig.height=5}
k          <- 14;
rst.4      <- weco.rule(rule=4, x=simu.data, k=k, sdx=sdx, mux=0);
simu.arl   <- weco.rl(rst.4);
hist(simu.arl, breaks = 100, freq = F,
     xlim=c(0, xmax), ylim=c(0,ymax),
     xlab="Running Length", ylab="Probability", main="Rule 3");
```

### Rule 5

$K$ out $K+1$ points out of 2 standard deviations from center line

```{r, eval=T, echo=TRUE, fig.width=6, fig.height=5}
k          <- 2;
rst.5      <- weco.rule(rule=5, x=simu.data, k=k, l=2, sdx=sdx, mux=0);
simu.arl   <- weco.rl(rst.5);
hist(simu.arl, breaks = 100, freq = F,
     xlim=c(0, xmax), ylim=c(0,ymax),
     xlab="Running Length", ylab="Probability", main="Rule 5");
```

### Rule 6

$K$ out $K+1$ points out of 1 standard deviations from center line

```{r, eval=T, echo=TRUE, fig.width=6, fig.height=5}
k          <- 4;
rst.6      <- weco.rule(rule=6, x=simu.data, k=k, l=1, sdx=sdx, mux=0);
simu.arl   <- weco.rl(rst.6);
hist(simu.arl, breaks = 100, freq = F, 
     xlim=c(0, xmax), ylim=c(0,ymax),
     xlab="Running Length", ylab="Probability", main="Rule 6");
```

### Rule 7

$K$ points in a row within 1 standard deviations from center line (either side)

```{r, eval=T, echo=TRUE, fig.width=6, fig.height=5}
k          <- 15;
rst.7      <- weco.rule(rule=7, x=simu.data, k=k, l=1, sdx=sdx, mux=0);
simu.arl   <- weco.rl(rst.7);
hist(simu.arl, breaks = 100, freq = F, 
     xlim=c(0, xmax), ylim=c(0,ymax),
     xlab="Running Length", ylab="Probability", main="Rule 7");
```

### Rule 8

$K$ points in a row > 1 standard deviations from center line (either side)

```{r, eval=T, echo=TRUE, fig.width=6, fig.height=5}
k          <- 8;
rst.8      <- weco.rule(rule=8, x=simu.data, k=k, l=1, sdx=sdx, mux=0);
simu.arl   <- weco.rl(rst.8);
hist(simu.arl, breaks = 100, freq = F, 
     xlim=c(0, xmax), ylim=c(0,ymax),
     xlab="Running Length", ylab="Probability", main="Rule 8");
```

## Multiple rules

Multiple rules can be combined as a list.

```{r, eval=T, echo=TRUE, fig.width=6, fig.height=5}
##rules 1 and 2
lst.rules  <- list(list(1, l=3),
                   list(2, k=9));
rst.m      <- weco.combine(simu.data, lst.rules=lst.rules);
simu.arl   <- weco.rl(rst.m);
hist(simu.arl, breaks = 100, freq = F, 
     xlim=c(0, xmax), ylim=c(0,ymax),
     xlab="Running Length", ylab="Probability", main="Multiple Rules");
```

## Plot results

A trace plot may be plotted as follows

```{r, eval=T, echo=TRUE, fig.width=6, fig.height=5}
plot(rst.m, start=1000, end=1500);
```

## Graphical user interface

The package provides a graphical user interface based on Shiny, which can be brought up by

```{r, eval=F, echo=TRUE, fig.width=6, fig.height=5}
run.weco();
```
